A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-02-01 doc/large_strain.tex
Update abstract

    In this work, we extend the application of matrix-free approaches to problems in solid mechanics and investigate different implementations of the finite-strain hyperelastic finite element tangent operator numerically.
    In order to improve the convergence behavior of iterative solvers, we also propose a method by which to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based implementation with an algebraic multigrid preconditioner {\color{red} on a single node} for a representative numerical example of a heterogeneous hyperelastic material in two and three dimensions.
  \end{abstract}

>>>>

    \changeJP{To date, there have been few assessments into the applicability of the matrix-free approach to problems in solid mechanics.
    In this work, we perform an initial investigation on the application of the matrix-free approach to problems in quasi-static finite-strain hyperelasticity to determine whether it is viable for further extension.
    Specifically, we study different numerical implementations of the finite element tangent operator, and determine whether generalized methods of incorporating complex constitutive behavior might be feasible.
    }
    In order to improve the convergence behavior of iterative solvers, we also propose a method by which to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based implementation with an algebraic multigrid preconditioner {\color{red} on a single node} for a representative numerical example of a heterogeneous hyperelastic material in two and three dimensions.
    \changeJP{We conclude that the application of matrix-free methods to finite-strain solid mechanics is promising, and that is it possible to develop numerically efficient implementations that are independent of the hyperelastic constitutive law.}
  \end{abstract}
